\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{a4paper, margin=1in}

\title{\textbf{Market Making and High Frequency Trading on Cardano \\--- Project Close-Out Report ---}}
\author{MuesliSwap Team}
\date{\\September 2025}

\begin{document}

\maketitle

\section*{Official Close-Out Summary}
\begin{itemize}[leftmargin=1cm]
    \item \textbf{Name of project and Project URL on Fund:}\\
    Market Making and High Frequency Trading on Cardano \\
    {\scriptsize\url{https://projectcatalyst.io/funds/10/osde-open-source-dev-ecosystem/market-making-and-high-frequency-trading-on-cardano}}

    \item \textbf{Project ID:} 1000104

    \item \textbf{Project managed by:} MuesliSwap Team

    \item \textbf{Project started in:} October 2023

    \item \textbf{Project completed in:} September 2025

    \item \textbf{Challenge KPIs and how the project addressed them:}
    \begin{itemize}
        \item \textbf{Liquidity:} Delivered a framework that enables decentralized market-making and boosts liquidity across Cardano DEXes.
        \item \textbf{Decentralization:} By releasing the code open-source, trading bot control is placed directly into the hands of the community.
        \item \textbf{Adoption:} Provided customizable templates and documentation, lowering barriers to entry for developers and users.
    \end{itemize}

    \item \textbf{Project KPIs and how the project addressed them:}
    \begin{itemize}
        \item \textbf{Open-source trading bot framework:} Designed and published a modular framework compatible with Cardano’s eUTXO model.
        \item \textbf{Integration with MuesliSwap:} Successfully connected the framework to MuesliSwap to demonstrate improved liquidity.
        \item \textbf{Customizable templates:} Released multiple templates for market-making, arbitrage, and liquidity mining strategies.
        \item \textbf{Community engagement:} Shared results and progress openly via GitHub and social channels.
    \end{itemize}

    \item \textbf{Key achievements:}
    \begin{itemize}
        \item Completed all four planned milestones: Research, Framework Development, Integration with MuesliSwap, and Customizable Templates.
        \item Released the first open-source trading bot framework specifically designed for Cardano.
        \item Established a foundation for future extensions into broader DeFi strategies.
    \end{itemize}

    \item \textbf{Key learnings:}
    \begin{itemize}
        \item Adapting traditional finance market-making models to Cardano requires careful handling of the eUTXO model.
        \item Open-source collaboration accelerates iteration and increases adoption.
        \item Providing ready-to-use templates greatly lowers the entry barrier for community participation.
    \end{itemize}

    \item \textbf{Next steps for the product or service developed:}
    \begin{itemize}
        \item Expand support for more Cardano DEX protocols beyond MuesliSwap.
        \item Develop advanced strategy modules (e.g., dynamic liquidity provision, cross-DEX arbitrage).
        \item Grow community contributions and maintain continuous updates.
        \item Explore partnerships with other Cardano projects to strengthen liquidity infrastructure.
    \end{itemize}

    \item \textbf{Final thoughts/comments:}\\
    This project successfully delivered a foundational open-source trading bot framework for Cardano, addressing the critical need for decentralized market-making. By enabling developers and traders to customize and deploy bots, we believe this work will enhance liquidity, foster innovation, and strengthen decentralization in the Cardano ecosystem.

    \item \textbf{Links to other relevant project sources or documents:}
    \begin{itemize}
        \item GitHub Repository:\\ \url{https://github.com/MuesliSwapTeam/muesliswap-market-maker}
        \item Close-Out Video:\\ \url{https://youtu.be/d6f2KLuWxRQ}
    \end{itemize}
\end{itemize}

\section{Introduction}
This report summarizes the development of the first open-source trading bot framework for Cardano. The project was initiated to address the absence of Cardano-compatible market-making bots and to empower the community with tools that enhance liquidity. Our goal was to design a robust, extensible, and open-source framework that supports default and customizable trading strategies.

\section{Project Overview and Milestones}
The project was executed over a period of five months and structured into four milestones:
\begin{enumerate}
    \item \textbf{Milestone 1 – Research and Requirement Analysis:}\\
    Produced a detailed report analyzing the requirements of trading bots under Cardano’s eUTXO model. Identified challenges and mapped out the framework architecture.

    \item \textbf{Milestone 2 – Framework Development:}\\
    Designed and released the first version of the open-source trading bot framework. Published the codebase with modular components for extensibility.

    \item \textbf{Milestone 3 – Integration with MuesliSwap:}\\
    Integrated the framework with MuesliSwap, demonstrating successful market-making activity and improved liquidity.

    \item \textbf{Milestone 4 – Customizable Templates:}\\
    Delivered multiple strategy templates, including market-making, arbitrage, and liquidity mining, enabling users to adapt bots to their needs.
\end{enumerate}

\section{Conclusion}
The successful completion of this project marks a significant step toward decentralized liquidity provision on Cardano. By creating an open-source, customizable trading bot framework, we have not only improved liquidity for MuesliSwap but also established a foundation for future cross-DEX strategies. We believe this framework will foster greater decentralization, adoption, and innovation within the Cardano DeFi ecosystem.

\bigskip

\noindent \textbf{For further information or to contribute, please refer to the links provided in the summary above.}

\end{document}